\chapter{Introduction}
\label{Introduction}

	‘PC Control’ is a mobile application software for parents to monitor and control their child PC remotely.  This application software enables one to monitor the remote machines desktop and thus control it with their android touch pointer. It can be used with Microsoft Windows to perform real time remote system control and administration tasks through different network environments.

	This software requires a TCP/IP connection between the server and the viewer, which works on LAN's as well as WAN's; even on internet if you provide a public IP address for your machine. User will need to know the IP address or name of the server when a viewer wants to connect to it. The initial handshaking consists of Client Initialization and Server Initialization messages When the connection between a client and a server is first established, the server begins by requesting authentication from the client using a challenge-response scheme, which typically results in the user being prompted for a username and password at the client end. 

	The server is designed to make the client as simple as possible, so it is usually up to the server to perform any necessary translations. Servers mirror the real display to a remote client, which means that the server is not 'multi-user'. It does, however, provide the primary user of a PC with remote access to their desktop. There will be an option to send messages to the server machine; these messages will notified on the server screen. In addition to the control through desktop; there will be shortcuts (i.e. single click actions) for power options.


\section{Purpose}

\label{Purpose}
	Through the project ‘PC Control’ mainly aim to develop a mobile client that can, permit remote network access to PC’s graphical desktop. The software must enable to get a view of the remote machine desktop and control it with your android touch pointer. It can be used to perform remote system control and administration tasks in Windows computational environments with assorted network capabilities.

\section{Scope}

\label{Scope}

	The ‘PC Control’ app have a lot of social significance, since nowadays educational systems demands use of PC with internet for even school students, which may expose the teenager students to the traps of Internet. This app helps the parents to monitor and control their wards remotely. The environments are fully networked for various purposes and everyone have smartphones. This project tries to develop an administration system which works upon existing network and android smartphones.

